Precise spiking motifs in neurobiological and neuromorphic data

### 2022-12-19 manuscript.tex
in sync

Spiking Neural Networks (SNNs)~\citep{maass_networks_1997} are natural candidates to use these precise temporal patterns in the brain. The approach which is currently most prominent in the SNN community is to use existing algorithms from machine learning and to adapt them to the specificity of spiking architectures~\citep{goltz_fast_2021} One such example is to adapt the successes of deep learning algorithms and to transfer the back-propagation algorithm to SNNs, as it is the most widely used to tune the weights of a classical (non spiking) Neural Network. In a nutshell, it considers the system as implementing an input / output function and iteratively updates the weights according to the direction and magnitude of the error's gradient. \change[Antoine]{Since the activation function of a spiking neuron is not differentiable,}{In deep learning, gradient is computed on the activation function and since spikes are not differentiable,} a recent popular approach consists in using a surrogate gradient}~\citep{neftci_surrogate_2019} to ``cross-compile'' a classical Neural Network to a spiking architecture~\citep{rueckauer_conversion_2017}. SNNs reach in some case a similar performance as their non spiking equivalent, for instance on the \remove[Antoine]{N-}MNIST dataset for categorizing digits in a stream of events~\citep{susi_nmnsd-spiking_2021}. \change[Antoine]{The main reason for adopting this approach instead of classical architectures is the possibility to benefit from dedicated neuromorphic low-energy hardware. 

>>>>

Spiking Neural Networks (SNNs)~\citep{maass_networks_1997} are natural candidates to use these precise temporal patterns in the brain. The approach which is currently most prominent in the SNN community is to use existing algorithms from machine learning and to adapt them to the specificity of spiking architectures~\citep{goltz_fast_2021} One such example is to adapt the successes of deep learning algorithms and to transfer the back-propagation algorithm to SNNs, as it is the most widely used to tune the weights of a classical (non spiking) Neural Network. In a nutshell, it considers the system as implementing an input / output function and iteratively updates the weights according to the direction and magnitude of the error's gradient. \change[Antoine]{Since the activation function of a spiking neuron is not differentiable,}{In deep learning, gradient is computed on the activation function and since spikes are not differentiable,} a recent popular approach consists in using a surrogate gradient~\citep{neftci_surrogate_2019} to ``cross-compile'' a classical Neural Network to a spiking architecture~\citep{rueckauer_conversion_2017}. SNNs reach in some case a similar performance as their non spiking equivalent, for instance on the \remove[Antoine]{N-}MNIST dataset for categorizing digits in a stream of events~\citep{susi_nmnsd-spiking_2021}. \change[Antoine]{The main reason for adopting this approach instead of classical architectures is the possibility to benefit from dedicated neuromorphic low-energy hardware. 
